---
title: "Lab1"
author: "Fabrizio Deza"
date: "`r Sys.Date()`"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Tasks 

## Task 1

Find the working directory 

```{r}
getwd()
```

## Task 2

Read in the DDT data 

```{r}
ddt <- read.csv("DDT.csv")
head(ddt)
```

## Task 3

  a. The qualitative variables are RIVER and SPECIES
  b. The quantitative variables are MILE< LENGTH< WEIGHT, and DDT 
  c. 3
  d. Subset the ddt data set so that we see only those obs with Species,
  LMBASS and Weight bigger than 800gms       
```{r}
test <- with(ddt, ddt[SPECIES=="LMBASS" & WEIGHT>800,] )
test
```
e. Subset the ddt data set so that we see only those obs where the river is SCM and DDT bigger than 4.0
```{r}
test1 <- with(ddt, ddt[RIVER=="SCM" & DDT>4,])
test1
```

  
  
## Task 4


```{r}
### Make a table of rivers
tb=with(ddt, RIVER)
tb

###Make a color coded barplot of the rivers
tbb <- table(ddt$RIVER)
barplot(tbb, main = "Rivers", col = rainbow(4))

### Make a table of the rivers crossed with the species of fish
rf <- table(ddt$RIVER, ddt$SPECIES)
rf

### Make a barplot of the rivers crossed with the species of fish 
barplot(rf, xlab="Number of species in each river", col=c("blue","red","green","orange"),legend=rownames(rf))

```

## Task 5

```{r}
### Mle a pie chart of Fish Species 
fspec <- table(ddt$SPECIES)
pie(fspec, col=1:3)

### Make a pie chart of RIVERS 
pie(tbb, col=1:4)

```

## Task 6

```{r}
### Make a boxplot of the variable DDT
boxplot(ddt$DDT, horizontal = TRUE, ylab="Fish",xlab="DDT")
### Make a boxplot of the variable WEIGHT
boxplot(ddt$WEIGHT, horizontal = TRUE, ylab="Fish",xlab="Weight")
### Make a boxplot of the variable LENGTH
boxplot(ddt$LENGTH,horizontal = TRUE, ylab="Fish",xlab="Length")

```

## Task 7
```{r}
### Make a coplot of length vs weight given river 
coplot(LENGTH~WEIGHT|RIVER, data=ddt)
### Make a coplot of DDT Vs Weight given species 
coplot(DDT~WEIGHT|SPECIES, data = ddt)
```

## Task 8
```{r}
library(ggplot2)

p <- ggplot(ddt, aes(x=SPECIES, y=WEIGHT, fill = RIVER))+geom_boxplot(position = position_dodge(1))
p + ggtitle("Fabrizio Deza")


vio <- ggplot(ddt, aes(x=RIVER, y=LENGTH, fill=SPECIES))+geom_violin()
vio + ggtitle("Fabrizio Deza")

sca <- ggplot(ddt, aes(x=WEIGHT, y=LENGTH, fill = SPECIES, color=SPECIES)) + geom_point()
sca + ggtitle("Fabrizio Deza")

```






